Foregrounds in Fourier Space for Redshifted 21~cm Observatories

### 2015-02-05 ms.tex
Continue editing section 5
from 8d355ca:
============

(*) Update figure5a.eps, figure5b.eps
(*) Add figure7.eps to git version control

In ms.tex,

(*) Continue editing section 5

Figure~\ref{fig:fhd_data} shows {\bf delay power spectra} from MWA data after deconvolution along the delay axis. The principal feature is the {\it foreground wedge}, whose boundaries, marked by white lines, increase linearly with light travel time proportional to baseline length. Note that the wedge is not filled out uniformly. Each baseline has a different orientation that determines the response to different objects in the sky. It is this variation that we will explore below.

@@

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/multi_baseline_fhd_delay_spectrum_snapshots.eps}
% \includegraphics[width=\linewidth]{f3.eps}
\includegraphics[width=\linewidth]{fig4.eps}
\caption{{\bf Delay power spectra} of two observations of the EoR field (RA = 0$^\textrm{h}$, Dec = $-30\arcdeg$) at an {\it off--zenith} pointing (top) when tiles have significant secondary lobes in the direction of the Galactic center and a {\it zenith} pointing (bottom) where secondary lobes are minimal and the Galaxy has set. {\bf In both cases, the delay spectra are phased to the zenith and thus the {\it foreground wedge} boundaries are symmetric around $\tau=0$}. For reference, the $k$--space equivalent of $\tau$ and $|\boldsymbol{b}|$, namely, $k_\parallel$ and $k_\perp$ are shown at the axes on the right and top respectively. White lines mark the boundaries of {\it foreground wedge} determined by light travel time across each baseline. Smooth spectrum objects predominantly reside in this {\it foreground wedge}. The logarithmic color scale (shown at the right) is common to both panels. \label{fig:fhd_data}}
\end{figure}

@@

With the aforementioned foreground model, and instrumental and observational parameters, we simulate visibilities using equation~\ref{eqn:obsvis}. Figure~\ref{fig:sim_data} shows the {\bf delay power spectra} from {\it off--zenith} and {\it zenith} pointings. Notice the qualitative agreement of amplitude and structure with those obtained from data shown in Figure~\ref{fig:fhd_data}. The Galactic center and the Galactic plane visible in the {\it off--zenith} pointing make it appear brighter in the {\it foreground wedge}.

\begin{figure}[htb]
\centering
% \includegraphics[width=\linewidth]{figures/v1_0/multi_baseline_sim_delay_spectrum_snapshots.eps}
% \includegraphics[width=\linewidth]{f7.eps}
\includegraphics[width=\linewidth]{fig8.eps}
\caption{Same as Figure~\ref{fig:fhd_data}, but generated from simulated visibilities using the model described in \S\ref{sec:modeling}. Note the similarity between the broad features to those in Figure~\ref{fig:fhd_data}. \label{fig:sim_data}}
\end{figure}

@@

These uncertainties are presented only to confirm the qualitative agreement already seen between Figures~\ref{fig:fhd_data} and \ref{fig:sim_data}. These estimates are conservative. A full treatment of all uncertainties and deviations from ideal behavior such as frequency dependent errors in tile power pattern \citep{ber15}, calibration \citep{dat10}, data corruption due to interference, anisoplanatic wide--field imaging and ionospheric effects \citep{int09} will bring the simulations much closer in agreement with observations, but is beyond the scope of this paper. {\bf Hereafter}, our primary objective is to explore in detail the foreground signatures embedded in the {\it foreground wedge}.

>>>>

% Figure~\ref{fig:fhd_data} shows {\bf delay power spectra} from MWA data after deconvolution along the delay axis. The principal feature is the {\it foreground wedge}, whose boundaries, marked by white lines, increase linearly with light travel time proportional to baseline length. Note that the wedge is not filled out uniformly. Each baseline has a different orientation that determines the response to different objects in the sky. It is this variation that we will explore below.

@@

% \begin{figure}[htb]
% \centering
% % \includegraphics[width=\linewidth]{figures/v1_0/multi_baseline_fhd_delay_spectrum_snapshots.eps}
% % \includegraphics[width=\linewidth]{f3.eps}
% \includegraphics[width=\linewidth]{fig4.eps}
% \caption{{\bf Delay power spectra} of two observations of the EoR field (RA = 0$^\textrm{h}$, Dec = $-30\arcdeg$) at an {\it off--zenith} pointing (top) when tiles have significant secondary lobes in the direction of the Galactic center and a {\it zenith} pointing (bottom) where secondary lobes are minimal and the Galaxy has set. {\bf In both cases, the delay spectra are phased to the zenith and thus the {\it foreground wedge} boundaries are symmetric around $\tau=0$}. For reference, the $k$--space equivalent of $\tau$ and $|\boldsymbol{b}|$, namely, $k_\parallel$ and $k_\perp$ are shown at the axes on the right and top respectively. White lines mark the boundaries of {\it foreground wedge} determined by light travel time across each baseline. Smooth spectrum objects predominantly reside in this {\it foreground wedge}. The logarithmic color scale (shown at the right) is common to both panels. \label{fig:fhd_data}}
% \end{figure}

@@

With the aforementioned foreground model, and instrumental and observational parameters, we simulate visibilities using equation~\ref{eqn:obsvis}. Figure~\ref{fig:fhd-sim-comparison} shows the {\bf delay power spectra} from {\it off--zenith} and {\it zenith} pointings obtained from MWA observations and modeling. Notice the qualitative agreement of amplitude and structure between the two. The Galactic center and the Galactic plane visible in the {\it off--zenith} pointing make it appear brighter in the {\it foreground wedge} as a branch with $\tau<0$.

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{figure7.eps}
\caption{Delay power spectra from MWA data (left) and modeling (right) for the {\it off--zenith} (top) and {\it zenith} (bottom) pointings. The modeling matches the data to a level consistent with the uncertainties in foreground models and the antenna beam. \label{fig:fhd-sim-comparison}}
\end{figure*}

@@

These uncertainties are presented only to confirm the qualitative agreement already seen between data and modeling in Figure~\ref{fig:fhd-sim-comparison}. These estimates are conservative. A full treatment of all uncertainties and deviations from ideal behavior such as frequency dependent errors in tile power pattern \citep{ber15}, calibration \citep{dat10}, data corruption due to interference, anisoplanatic wide--field imaging and ionospheric effects \citep{int09} will bring the simulations much closer in agreement with observations, but is beyond the scope of this paper. {\bf Hereafter, our focus} is to explore in detail the foreground signatures embedded in the {\it foreground wedge} of the MWA instrument.
